% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Steven Diviney} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{empty} % set pagestyle for the document

\begin{document} 
\begin{resume}

\begin{flushright}
   Steven Diviney \\
   14 Strand Road \\
   Sutton \\
   Dublin 13 \\
   Ireland \\
   0863807768 \\
   divoapple@gmail.com \\* \vspace{10 mm}
\end{flushright}
\begin{flushleft}
 
August 19th, 2014\\*\vspace{10 mm}
Dear Sir/Madam
\end{flushleft}
<<<<<<< HEAD
I am writing in response to your advertised software engineering position at MatserCard Ireland.

I graduated from Trinity College Dublin in November 2013 with a Masters in Computer Science and a first class honors B.A.Mod in Computer Science. I have interned in MasterCard and IBM. Since graduating I have spent my time traveling and working part time.\\

I am particularly interested in the advertised post because I would love to work for one of the most successful companies in the I.T. industry. I very much enjoyed my time in MasterCard. The Fraud Rules Manager Rules Authoring team was only beginning in Dublin towards the end of my internship and I was very interested in the type of work they were doing. \\
=======
I am writing in response to your advertised Graduate Software Engineer position at Murex.

I graduated from Trinity College Dublin in November 2013 with a Masters in Computer Science and a first class honors B.A.Mod in Computer Science. I have interned in MasterCard and IBM. Since graduating I have spent my time traveling and working part time.

I have a lot of experience writing Java code in a production environment and consider myself very proficient in its use. I also have a good amount of experience in Python, SQL, C/C++, JavaScript, Objective-C and Android development among others. I have completed large projects using each of these languages, both personal and at university. 
>>>>>>> d987532fdfdaba1d93c2a71a2b8a29d2722d6b5d
I feel I am suited to the position because I have very good teamwork, communication and presentation skills. In addition I have very good technical skills as outlined in my curriculum vitae. I more than meet all of the requirements outlined.
\\*
\\*
I have enclosed my curriculum vitae. If you need any further information, please do not hesitate to contact me. I look forward to hearing from you.\\*

\begin{flushleft}
Yours faithfully\\\vspace{10mm}

Steven Diviney\\
\end{flushleft}

\end{resume}
\end{document}
