% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Steven Diviney} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 

\thispagestyle{empty} % this page does not have a header
\pagestyle{empty}
\name{Steven Diviney}
\address{14 Strand Road\\
Sutton\\
Dublin 13\\
00 353 86 3807768\\
divines@tcd.ie}






\begin{resume}
\vspace{0.1in}
\moveleft.5\sectionwidth\centerline{Objective: Graduate Computer Science student looking for career opportunities in a reputed organization.}  


\section{Education}
\vspace{0.1in} 

    Trinity College, Dublin, (MCS) Master in Computer Science, 2012 - 2013
 
    Trinity College, Dublin, BA(Mod) Computer Science, 2008 - 2012\\ 
    Graduated with I.I
 
    Sutton Park, Sutton, Dublin, 2002 - 2008,\\
    Leaving certificate obtained in 2008. 450 GCSE\\
    points in ICT obtained in 2006.\\
    

\section{Experience} 
\vspace{0.1in}

    {\bf Trim Transport Ltd, 2013 - Present} Notable aspects include; Developing and maintaining an invoicing system, secretarial duties, vehicle maintenance and preparing cargo for shipment.

    {\bf Masters Thesis, 2013} My thesis, titled: Browser Based Categorization of Data Towards Automated Visualization, attempted to create a system to automatically visualize an arbitrary dataset. Data visualization as a tool to reinforce human cognition is an interest of mine, particularly as the volume of data being generated is growing so rapidly. Usually visualizations are bespoke or at the very least the tools used to generate them are complex and require additional information, usually provided by an expert. My system generated visualizations using only the input data. No additional meta-data was required. Several markers were obtained by analyzing the structure of the data. These values were then used to select a specific visualization. The effectiveness of the visualization was the key concern. There exists a good body of research detailing what makes a visualization effective, the results of which were integrated into my system.\\
    Overall I determined that such a system can be effective at creating useful visualizations, but its effectiveness diminishes as the data becomes more complex.


    {\bf MasterCard Ireland, 2012} Seven month internship as part of my degree program. Primary worked as part of the InControl team. InControl is a service offered by MasterCard that allows their users to manage various credit card controls, such as spend limits based on amount, geography, time and many others. I was primary responsible for maintaining and updating a testing tool used by QA to interface with the InControl service to test it. I worked closely with both the InControl development team and QA team. The tool I was responsible for interfaced with the entire system so I became quite proficient at tracking bugs through InControls multiple components. \\
    This work was quite broad. I gained valuable experience with the entire technology stack, developing user interfaces right through to stored procedures in SQL executed on remote hosts. The technologies used were primary Java and Oracle SQL.\\
    Towards the end of the internship I was also tasked with developing a prototype for a new service MasterCard were looking to introduce. The work was done in co-junction with another intern with direction supplied by my manager and various developers. The prototype was a web application built using the Spring Framework, a popular inversion of control container.
     
    {\bf IBM Ireland, 2011 }Summer internship for 3 months at IBM Ireland as part of their Extreme Blue internship program. Worked on a mobile web application as part of a team of four. The project was voted second out of over twenty at the end of the internship. As well as creating the application we were required to give a weekly update presentation to our managers and co-workers. Developed skills in computer programming, teamwork, and communication with management and architects in order to design and plan the project, in addition to making sure the project was on track and mile-stones were being met.\\
    
 
    {\bf GeSCI, 2010} Co-developed open-source software to assist with the calculation of ICT costs across a country. The software is now deployed in several Ministry's of Education across Africa, distributed freely from GeSCIs website. I was responsible for creating the front-end. Worked as part of a team of six, three programmers and three managers / architects. Developed skills in computer programming and teamwork. In addition to my role as programmer I attended most of the meetings with the client in order to ensure what we were building was what they wanted. Developed skills in translating user requirements into a final design that was implemented.

    {\bf Dangerous Goods Safety Advisor, 2010 - Present} Responsible for ensuring that three organizations adhere to the requirements set out by the European Agreement concerning the International Carriage of Dangerous Goods by Road. Notable aspects include inspection of sites to ensure regulations are being adhered too, consultation with the organizations if regulations are not being met and the submission of an annual report to the HSA. Developed skills include organizing meetings with clients and ensuring that the applicable laws are being adhered too. 
 
    {\bf Freelance Graphic Design} Notable aspects include; Consulting with clients in order to assess their requirements. Creating of drafts based on clients requirements. Refining draft into final copy.
 
    
 


     
\section{Skills and Interests} 
\vspace{0.1in}
 {\bf Operating Systems}
    \begin{itemize} % Use \item[] to prevent a bullet from appearing
      \item[] GNU/Linux, primarily Debian based, very good working and theoretical knowledge. Have used Debian as a primary OS for over 8 years and enjoy learning about the design of UNIX systems in general.\\
        Windows 7, Vista, XP, very good working knowledge.
      \end{itemize}
{\bf Programming} 
       \begin{itemize}
        \item[] Very good level of experience programming in Java.\\
        I am very comfortable working in C/C++, Python and Javascript.
        I have a good knowledge of OOP concepts and design patterns as well as functional, imperative and declarative programming paradigms.  
        In addition I have completed projects written in C\#, Bash, HTML5, SQL (Oracle DBMS, IBM DB2 and MySQL), PHP, Haskell, Prolog and VHDL. I enjoy programming in my free time and have many personal projects. These range from micro-controller projects, generative artwork, Ajax driven and static web-design, design of various database schema, JSON parsers, network programming and Android apps.\\
        Also have many projects as a result of university course work. These range from simple compilers, logic puzzles, implementation of various data structures, multi-threaded programs, XML and JSON parsers, SSE programming, a network proxy server, a web-server, an email server and client and various database schema.
    \end{itemize}

    {\bf  Teamwork} 
        \begin{itemize}
        \item[]  Very good teamwork skills. In addition to developing teamwork skills during my work experience and college projects I have also developed good communication skills during my time at university in general. Almost every project is designed to some degree as a group and implemented as a group or in isolation. I approach each project with enthusiasm, particularly if it's something new and feel my course work marks reflect this.
       \end{itemize} 

  {\bf Design} 
        \begin{itemize}
        \item[] I have a good knowledge of graphic design concepts and the technical knowledge on how to apply them. This applies to both graphic and user interface design.
       \end{itemize}

   {\bf  Electronics} 
        \begin{itemize}
        \item[]  I have some experience working with embedded electronics, primarily the Atmel AVR series of chips. This is a personal interest of mine which I have been able to expand on during my time in university. I have put together several small projects using the Arduino platform in addition to stock AVR chips. Also have experience with setup and configuration of reasonably complex LANs.
       \end{itemize} 

 
\section{Referees}
\vspace{0.1in} 
 
   Dr. Owen Conlan\\
   Assistant Professor\\
   School of Computer Science and Statistics\\
   Trinity College Dublin\\
   E-mail: Owen.Conlan@cs.tcd.ie\\
   \\
   \\
   Dr. Peter Groarke\\
   Consultant Software Engineer, Risk Systems\\
   MasterCard Technologies Dublin\\
   E-mail: peter\textunderscore groarke@mastercard.com\\
   \\
   \\
   Mr. Mark Gargan\\
   Mobile Software Development Manager and Architect\\
   IBM Ireland\\
   E-mail: mark.gargan@ie.ibm.com



    
 

\end{resume}
\end{document}






























